How Significant was WW2 in the Development of the Computer?

### 2017-02-20 Draft 2/Section 2 - Turing Machines.tex
Major changes to sec2, added sec3
Appendages & corrections & clarifications for sec2, first few subsections
of sec3

\renewcommand{\arraystretch}{1.5}

\begin{document}

@@

\subsubsection{Examples of simple Finite State Machines}\label{sec:FSMintro}
The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output (much like random access memory on a modern computer); secondly, a set of states known as \textit{m}-configurations, each of which contain operations to be performed on the tape, and the \textit{m-configuration} that the FSM moves to. An example description of such a set would be:

@@

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
    \hhline{====}
    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{e}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
    \hhline{----}
    \multirow{2}{*}{$\mathbb{A}$} & \texttt{1} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
                                  & \texttt{1} &                                  & $\mathbb{B}$ \\
    \hhline{----}
    \multirow{2}{*}{$\mathbb{B}$} & Any        & R, R                             & $\mathbb{B}$ \\
                                  & None       & P\texttt{1}, L                            & $\mathbb{C}$ \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{C}$} & \texttt{x} & E, R                             & $\mathbb{B}$ \\
                                  & \texttt{e} & R                                & $\mathbb{D}$ \\
                                  & None       & L, L                             & $\mathbb{C}$ \\
    \hhline{----}
    \multirow{2}{*}{$\mathbb{D}$} & Any        & R, R                             & $\mathbb{D}$ \\
                                  & None       & P\texttt{0}, L, L                         & $\mathbb{A}$ \\
\end{tabu}

@@

\subsubsection{\textit{M}-functions}\label{sec:mfunctions}

@@

\subsubsection{Data Structures and Pointers}

@@

\subsubsection{Scripted Configurations}
As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions. We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multirow{2}{*}{$\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O})} 
                                                                                       & \textit{c} & - & \textfrak{I} \\
                                                                                       & Other & - & \textfrak{O} \\ 
    \hhline{====}
    $\mathbb{ifp}$(\textit{r}, \textit{c}, \textfrak{I}, \textfrak{O}, \textfrak{E}) & - & - & $\mathbb{fl}$($\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O}), \textfrak{E}, \textit{r}) \\
\end{tabu}

@@

\begin{lstlisting}
ifp(r, c, I, O, E) = fl(r,
    if(c, I, O), E
)
\end{lstlisting}

While this syntax is more concise, it is still somewhat obfuscated. Therefore, we will use our function method to define what is effectively a list of commands for the machine which will be executed in order. The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that

>>>>

\renewcommand{\arraystretch}{1.5}p

\lstdefinelanguage{Turlang}
{
  morekeywords={
    function,
    bool,
    int,
    and,
    or,
    not,
    xor
  },
  sensitive=true, % keywords are not case-sensitive
  morecomment=[l]{//}, % l is for line comment
  morecomment=[s]{/*}{*/}, % s is for start and end delimiter
  morestring=[b]" % defines that strings are enclosed in double quotes
}
\lstset{language=Turlang}
\begin{document}

@@

\subsection{Examples of simple Finite State Machines}\label{sec:FSMintro}
The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output; secondly, a set of states known as \textit{m}-configurations, each of which contain operations to be performed on the tape, and the \textit{m}-configuration that the FSM moves to. An example description of such a set would be:

@@

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
    \hhline{====}
    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{0}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
    \hhline{----}
    \multirow{2}{*}{$\mathbb{A}$} & \texttt{0} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
                                  & \texttt{1} &                                  & $\mathbb{B}$ \\
    \hhline{----}
    \multirow{2}{*}{$\mathbb{B}$} & Any        & R, R                             & $\mathbb{B}$ \\
                                  & None       & P\texttt{1}, L                            & $\mathbb{C}$ \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{C}$} & \texttt{x} & E, R                             & $\mathbb{B}$ \\
                                  & \texttt{e} & R                                & $\mathbb{D}$ \\
                                  & None       & L, L                             & $\mathbb{C}$ \\
    \hhline{----}
    \multirow{2}{*}{$\mathbb{D}$} & Any        & R, R                             & $\mathbb{D}$ \\
                                  & None       & P\texttt{0}, L, L                         & $\mathbb{A}$ \\
\end{tabu}

@@

\subsection{\textit{M}-functions}\label{sec:mfunctions}

@@

\subsection{Data Structures and Pointers}

@@

\subsection{Scripted Configurations}
As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions. We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multirow{2}{*}{$\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O})} 
                                                                                       & \textit{c} & - & \textfrak{I} \\
                                                                                       & Other & - & \textfrak{O} \\
\end{tabu}

@@

\begin{lstlisting}
ifp(r, c, I, O, E) = fl(r,
    if(c, I, O), E
)
\end{lstlisting}
While this syntax is more concise, it is still somewhat obfuscated. Therefore, we will use our function method to define what is effectively a list of commands for the machine which will be executed in order. The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that function in order for the functions to be called sequentially. The following function main() defines variables \textit{var1} and \textit{var2}, and sets \textit{var2} to be not \textit{var1}, or \texttt{1}.

\begin{lstlisting}
function main() {
	bdef(var1)
	bdef(var2)
	bneg(var1, var2)
}
\end{lstlisting}
For clarity, I have ignored error handling (i.e. omitted the E argument). This is equivalent to:

\begin{lstlisting}

main(C, E) = bdef(var1,
    bdef(var2,
        bneg(var1, var2, C, E), E
    ), E
)

\end{lstlisting}
With arguments for continuity and simple error correction. This, in turn, can be simplified into a table.

Furthermore, we can simplify certain functions to have their own specific syntax. In the case of definitions, "\lstinline{bdef(var)}" shall be abbreviated to "\lstinline{bool var}";
